Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
Minor spelling errors.

\noindent where $I$ is the inertia moment of satellite about its mass
center, $\tau_{C}$ is the control torque applied by thusters, and $\theta$
is the controlled attitude angle.  Normalizing Eq.~\eqref{eq:satelliteode}
by defining the control signal $u=\frac{\tau_{C}}{I}$ and taking Laplace
transform, the following $s$-domain transfer function $G(s)$ is obtained
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}

>>>>

\noindent where $I$ is the inertia moment of satellite about its mass
center, $\tau_{C}$ is the control torque applied by thrusters, and $\theta$
is the controlled attitude angle.  Normalizing Eq.~\eqref{eq:satelliteode}
by defining the control signal $u=\frac{\tau_{C}}{I}$ and taking Laplace
transform, the following $s$-domain transfer function $G(s)$ is obtained
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}
